% Extrait du script de recherche

\label{Script}

\begin{minted}[linenos, breaklines=true]{python}    
    import os  # Allows interaction with the computer, regardless of its operating system.
    import sys  # Allows for the argument to be called directly from the command line.
    from bs4 import BeautifulSoup
  
    def parse(corpus):
        """ Parses the given corpus.
        Parameter
        ---------
        corpus
           Absolute path for the corpus.
           Corresponds to "arg1" in the command line.
        """
        for root, dirs, files in os.walk(corpus):
            for filename in files:
                with open(os.path.join(root, filename), 'r', encoding='UTF-8') as xml_file:
                # Opens the files in 'read' mode and stores the opened file in a variable called 'xml_file'.
                    xml_content = xml_file.read()
                    # The 'xml_content' variable stores the content of the file opened in 'xml_file' with the '.read()' method.
                    soup = BeautifulSoup(xml_content, 'xml')
                    # Creates a 'soup' object, which parses 'xml_content' with the XML parser included in the BeautifulSoup library.
                    yield filename, soup
                    # The 'yield' statement suspends the execution of the function to return a result, and then resumes execution instead of starting over every time.

   
    def missing_tag(tag):
        """ Finds the files from which the element is missing.
        Parameter
        ---------
        tag : str
            Name of the researched element, between quotation marks.    
        Returns
        -------
        set()
            Set containing the names of the files from which the given element is missing.
        """
        files_missing_tag = set()
        for filename, soup in parse(sys.argv[1]):
            # Uses the 'parse' function to parse the corpus provided by 'arg1' in the command line.
            if not soup.find_all(tag):
                files_missing_tag.add(filename)
                # Adds the name of the file to the set if the '.find_all()' method does not find any occurrence.
                print(filename)
    # Example --> missing_tag("catRef")
\end{minted}